Evaluation of classical correlation functions from 2/3D images on CPU and GPU architectures: introducing CorrelationFunctions.jl

### 2023-09-07 paper-correlations.tex
F_{ss} is NOT a probability

There are different types of correlation functions that in general describe some
probabilities. The main parameter of any correlation function is the number of
points that are utilized to evaluate such a probability. While so-called
$n$-point probability function \cite{Torquato_book} will completely describe any
structure in the limit of $n \rightarrow$ number of voxels/pixels on the image,
computing or storing such a function is not practical. Based on information
content, it was shown that increasing the number of point $n > 2$ only
marginally improves the quality of the structure quantification and these
improvements decay with increasing $n$ \cite{yao1993high,Gommes2}. For
stochastic reconstruction purposes computation of higher-order statistics will,
arguably, not be balanced by increased number of points, but this is the topic
of active research \cite{skolnick2021,cherkasovIC}. For aforementioned reasons,
we mainly focus on 2-point statistics, leaving the possibility to include higher
order CFs in the future work. The simplest 2-point probability function ($S_2$
or autocorrelation) actually arise from small angle scattering experiments and
measures the probability that both ends of line segment with a given length fall
into the same phase. Other types include the probability of a whole line segment
to fall into the phase ($L_2$ function) or to lie on the interface between
phases ($F_{ss}$ function), and mainly originated from aforementioned bounds on
physical properties such as permeability and elasticity. The general idea of
computation of different 2-point CFs is shown in \cref{fig:functions}. All major
details and numerous analytical cases can be found in seminal work of Torquato
\cite{Torquato_book}. To all CFs described in this book and applicable to
digital images we shall refer to as classical correlation functions.

>>>>

There are different types of correlation functions that in general describe some
probabilities. The main parameter of any correlation function is the number of
points that are utilized to evaluate such a probability. While so-called
$n$-point probability function \cite{Torquato_book} will completely describe any
structure in the limit of $n \rightarrow$ number of voxels/pixels on the image,
computing or storing such a function is not practical. Based on information
content, it was shown that increasing the number of point $n > 2$ only
marginally improves the quality of the structure quantification and these
improvements decay with increasing $n$ \cite{yao1993high,Gommes2}. For
stochastic reconstruction purposes computation of higher-order statistics will,
arguably, not be balanced by increased number of points, but this is the topic
of active research \cite{skolnick2021,cherkasovIC}. For aforementioned reasons,
we mainly focus on 2-point statistics, leaving the possibility to include higher
order CFs in the future work. The simplest 2-point probability function ($S_2$
or autocorrelation) actually arise from small angle scattering experiments and
measures the probability that both ends of line segment with a given length fall
into the same phase. Other types include the probability of a whole line segment
to fall into the phase ($L_2$ function) or ``pointing'' with its ends to the
same cluster ($C_2$ function) and mainly originate from aforementioned bounds on
physical properties such as permeability and elasticity. The general idea of
computation of different 2-point CFs is shown in \cref{fig:functions}. All major
details and numerous analytical cases can be found in seminal work of Torquato
\cite{Torquato_book}. To all CFs described in this book and applicable to
digital images we shall refer to as classical correlation functions.
